---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PLreg

<!-- badges: start -->
<!-- badges: end -->

The **PLreg** package allows fitting power logit regression models. Diagnostic tools associated with the fitted model, such as the residuals, local influence measures, leverage measures, and goodness-of-
fit statistics, are implemented. 

## Installation

You can install the development version of PLreg from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ffqueiroz/PLreg")
```

## Main functions

#### <tt>dPL</tt>, <tt>pPL</tt>, <tt>qPL</tt>, and <tt>rPL</tt>

Currently, the $\textbf{PLreg}$ package includes 7 members of the power logit class of distributions: the power logit normal, power logit Student-t, power logit type II logistic, power logit power exponential, power logit sinh-normal, power logit hyperbolic and power logit slash distributions. The package provides the  <tt>dPL</tt>, <tt>pPL</tt>, and <tt>qPL</tt> functions  to compute the probability density function, cumulative distribution function and quantile function of the power logit distribution. Also, the <tt>rPL</tt> function may be used to generate random samples from power logit distributions. The basic usages of these functions are:

```{r usage functions, eval=FALSE}
dPL(x, mu, sigma, lambda, zeta = 2, family, log = FALSE)

pPL(q, mu, sigma, lambda, zeta = 2, family, lower.tail = TRUE, log.p = FALSE)

qPL(p, mu, sigma, lambda, zeta = 2, family, lower.tail = TRUE, log.p = FALSE)

rPL(n, mu, sigma, lambda, zeta = 2, family)
```

#### <tt>PLreg</tt> 

The main function of the $\textbf{PLreg}$ package is <tt>PLreg()</tt>, which allows to fitting power logit regression model to proportional data; this explains the name. The arguments of <tt>PLreg()</tt> are:

```{r PLregfunction, eval = FALSE}
PLreg(formula, data, subset, na.action, family = c("NO", "LO", "TF", "PE", "SN", "SLASH", "Hyp"), 
      zeta = NULL, link = c("logit", "probit", "cloglog", "cauchit", "log", "loglog"), 
      link.sigma = NULL, type = c("pML", "ML"), control = PLreg.control(...), 
      model = TRUE, y = TRUE, x = FALSE, ...)
```

The <tt>PLreg()</tt> function returns an object of class "<tt>PLreg</tt>", similar to "<tt>betareg</tt>" and "<tt>glm</tt>" objects, for which some methods available. The <tt>summary()</tt> method returns a standard output, with coefficient estimates, standard errors, partial Wald tests and p values for the regression coefficients, the overall goodness-of-fit measure, the pseudo $R^2$, etc.. The <tt>type</tt> argument in <tt>summary()</tt> specifies the type of residuals included in the output; currently three residuals are supported: <tt>"standardized"</tt>, </tt>"quantile"</tt> and <tt>"deviance"</tt>. The <tt>plot()</tt> method draws graphs for diagnostic and influence analyses.

#### <tt>extra.parameter</tt> 

An important function in the $\textbf{PLreg}$ package is <tt>extra.parameter()</tt>. It can be used to estimate the extra parameter of some power logit models. The basic usage is:

```{r extraparameter, eval = FALSE}
extra.parameter(object, lower, upper, grid = 10)
```

## Example

```{r example}
library(PLreg)
## basic example code
```

In the following, an example is presented to illustrate the capacities of $\textbf{PLreg}$ package. We use the <tt>bodyfat_Aeolus</tt> data set, available in the package.
```
help(bodyfat_Aeolus, package = "PLreg")
```

The response variable is <tt>percentfat</tt> and the covariates are the sex of the sampled bat (<tt>sex</tt>), the hibernation time (<tt>days</tt>) and the year that the bat was sampled (<tt>year</tt>). We start by fitting a power logit power exponential regression model with constant dispersion and $\zeta = 2$. To select a suitable value for $\zeta$, use the <tt>extra.parameter()</tt> function as follows.

```{r bodyfatreg_zeta, eval  = FALSE}
fitPL_PE_start <- PLreg(percentfat ~ days + sex + year, data = bodyfat_Aeolus,
              family = "PE", zeta = 2)
extra.parameter(fitPL_PE_start, lower = 1, upper = 2.5)
```

Then, fit the model with the chosen value for $\zeta$.

```{r bodyfatreg, eval = TRUE}
fitPL_PE <- PLreg(percentfat ~ days + sex + year, data = bodyfat_Aeolus,
              family = "PE", zeta = 1.7)
summary(fitPL_PE)
```

The goodness of fit is assessed using diagnostic graphs through the plot method.

```{r bodyfat_diagnostics, eval = FALSE}
plot(fitPL_PE, which = 1:4)
```

Further details and examples on the R package $\textbf{PLreg}$ can be found using the help on R by typing:

```
help("PLreg")
```

## Reference

Queiroz, F.F. and Ferrari, S.L.P. (2022). Power logit regression for modeling bounded data. 
